Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Fix naming convention boreal -> subarctic

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and assess the monthly significance of the ozone concentration anomalies in 2018/19 (Fig.~\ref{fig:anomalies_svanvik}d)). The resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month in Fig~\ref{fig:data_svanvik_2018_2019}. Negative deviations from climatology are shown as a negative percentage. Note that missing bars for certain months are both due to data availability and anomalies not meeting the $1\sigma$ criteria. The the star indicates resulting anomalies after the reconstruction of missing data in July. In April/May 2018, ozone was significantly enhanced, while no significant enhancement is found in 2019. In both years, ozone concentrations were significantly lower than average in November. These results mean, that the extensive forest fires in Sweden did not lead to a significant enhancement in \chem{[O_3]} at Svanhovd in 2018.

@@

We define two different hypothetical temperature acclimation: \emph{Boreal} and \emph{cold}. The most extreme of the two acclimations is \emph{boreal}. For either, we assume that the hypothetical species are more tolerant to cold conditions and shift $f_\mathrm{T}$ towards colder temperatures accordingly. We construct \emph{cold} as representative for a species that is more tolerant to cold temperatures, but slightly less efficient at warm temperatures compared to MM. In the same way, \emph{boreal} refers to a hypothetical species which is very tolerant to cold but is sensitive to high temperatures, and most efficient at cool temperatures ($T_\mathrm{opt}$ close to the climatological mean temperature of 1992--2000). For perennial grassland the resulting response functions are depicted together with the PDF of temperature in Fig.~\ref{fig:f_temp_grassland}a).

Norway spruce was experimentally found to be active already at rather low air temperatures and could reach $60\,\unit{\%}$ photosynthetic activity as early as \unit{doy}~100 \citep{TB:Kolari2007, TP:Wallin2013}. Based on the time series of observed \chem{CO_2} uptake and temperature at two observation sites in Southern ($\rightarrow$ \emph{cold}) and Northern ($\rightarrow$ \emph{boreal}) Finland \citep{TB:Kolari2007}, we estimate $10\,\unit{^\circ C}\le T_\mathrm{opt} \le 15\,\unit{^\circ C}$. We assume a similar acclimation for deciduous trees. All bespoke temperature parameters are listed in Table~\ref{tab:sensitivity_tests_temp}.\\

@@

\begin{table}[t]
  \caption{Bespoke temperature parameterizations. MM refers to mapping manual \citep{GCB:Mills2011,ICP:MappingManual2017}.}
  \label{tab:sensitivity_tests_temp}
  \begin{tabular}{llrrr}
    \tophline
    Species & type & $T_\mathrm{min}$ & $T_\mathrm{opt}$ & $T_\mathrm{max}$ \\
    \middlehline
    \multirow{3}{*}{Deciduous tree} & MM & 5 & 20 & 100\\
    & Boreal & 0 & 10 & 100\\
    & Cold & 5 & 15 & 100\\
    \middlehline
    \multirow{3}{*}{Coniferous tree} & MM & 0 & 20 & 100\\
    & Boreal & 0 & 10 & 100\\
    & Cold & 0 & 15 & 100\\
    \middlehline
    \multirow{3}{*}{Perennial grassland} & MM & 10 & 24 & 36\\
    & Boreal & 0 & 10 & 24 \\
    & Cold & 5 & 15 & 36\\
    \bottomhline
    \end{tabular}
\end{table}

@@

As indicated above, a better acclimation will result in a higher average $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$. To quantify the resulting bespoke parameterizations, we propose the following metric. For a generic GS (May--August), we compute climatological average and standard deviation of $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$ (Eq.~(\ref{eq:stomatal})) at noon (averaged over $11\,\unit{am}-1\,\unit{pm}$ local time) and in the morning (averaged over $5-9\,\unit{am}$ local time). We presume that relative stomatal conductance of around noon (highest light intensity) and in the early morning (lower intensities) are good proxies for \chem{CO_2} uptake efficiency. Our arbitrary optimization target is $60\,\unit{\%}$. Additional constrains are a small deviation between noon and morning and a low standard deviation indicating a higher robustness to interannual variability of growing conditions. For simplicity, we neglect the dependency on SWP in this regard. From the results shown in Fig.~\ref{fig:javis_func_opt_mean}, we identify boreal, PPFD0.8 as the best acclimation for all hypothetical species or PFTs alike. As expected due to the small adjustments, coniferous trees display the lowest deviation between the different types of parameterizations, while the divergence for perennial grassland is substantial as response to the stronger proposed temperature acclimation.

@@

For deciduous trees (Fig.~\ref{fig:pody_rel}a) all simulations exceed the CL by $5-25\,\unit{mmol\,\chem{O_3}\,m^{-2}}$. Deciduous trees display the largest variance of ozone uptake among all species or PFTs ($10-31\,\unit{mmol\,\chem{O_3}\,m^{-2}}$). In particular, the sensitivity to the light threshold is especially pronounced, e.g. $\Delta\mathrm{POD_1} = ^{+2.5}_{-3.6}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in case of the boreal type without bespoke GS in 2019. Without bespoke GS, 2018 displays a higher ozone damage risk than 2019. However, taking the later start and overall shorter GS in 2018 into account, this is reversed for the boreal acclimation type. This can be partly explained by very high light response factors (over $f_\mathrm{light}>0.8$) in the beginning of the GS in these simulations. Whether this is a bug or a feature of the $\mathrm{DO_3SE}$ model is not clear. SWP induced reduction in ozone uptake is only effective in 2018 and without bespoke GS. The temperature acclimation dependent bias in ozone uptake deduced for bespoke GS ranges between $(1.4-3.6)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(2.7-7.7)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+1.6}_{-2.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+1.9}_{-2.7}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

For coniferous trees (Fig.~\ref{fig:pody_rel}b), most simulations slightly exceed the CL ($0-10\,\unit{mmol\,\chem{O_3}\,m^{-2}}$). Coniferous trees' acclimation to prevailing temperatures was already good from the beginning and therefore the least biased of the generic MM parameterization. Coniferous trees display a medium sensitivity to the variation in the light threshold, e.g. $\Delta\mathrm{POD_1} = ^{+1.7}_{-1.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in case of boreal type without bespoke GS in 2018. Taking the bespoke GS into account, we find a higher ozone uptake in 2019 for all bespoke temperature response functions. The overall bias deduced from bespoke GS for boreal and cold types with respect to MM ranges between $(0.5-1.0)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(2.0-3.3)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+1.0}_{-0.8}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+1.3}_{-1.0}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

For perennial grassland (Fig.~\ref{fig:pody_rel}c), all simulations with bespoke GS stay below the CL. Perennial grassland shows the smallest ozone uptake, but a similarly large bias as deciduous trees. We also find a reversal for predicted ozone damage risk in $\mathrm{POD_1}$ between 2018 and 2019 for the boreal type. Perennial grassland shows the lowest sensitivity to the light threshold and SWP is only relevant without bespoke GS. The overall bias deduced from bespoke GS for boreal and cold types with respect to MM ranges between $(2.2-3.4)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(4.4-6.4)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+0.3}_{-0.2}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+0.3}_{-0.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig11}
  \caption{$\mathrm{DO_3SE}$ modeling results for $\mathrm{POD_1}$ with default parameterization (MM) and bespoke parameters for Svanhovd. Bespoke parameterizations include temperature response functions for boreal, cold and light thresholds (PPFD0.8, PPFD1.2) at the end of a MM GS (lighter hue and dotted lines) and the estimated GS for Svanhovd (2018, 2019). (a) Deciduous tree; (b) coniferous tree; (c) perennial grassland. The dashed horizontal lines indicate critical levels defined in \citet{ICP:MappingManual2017,ESPR:Hayes2021} for each species, respectively.}
  \label{fig:pody_rel}
\end{figure}

We estimated the biomass reductions in accordance to the CLs in \citet{ICP:MappingManual2017, ESPR:Hayes2021} for the most extreme temperature acclimation (\emph{boreal}) for each bespoke PFT. The estimates are listed in Table~\ref{tab:biomass_reduction}. The reported range in uncertainty corresponds to the maximum deviation defined by the $\pm 20\,\unit{\%}$ variation of the extent of stomatal opening at low light intensities with SWP=on. For deciduous trees and perennial grassland, substantial reductions in total biomass in comparison with the default generic MM parameterizations are predicted for both years. Coniferous trees are the least affected and the magnitude of total biomass reduction is independent of the choice of the parameterization within given uncertainties. This may reflect the more comprehensive research on this species or PFT feeding into the generic MM parameterization. The systematic deviation for deciduous trees is one order of magnitude larger than for coniferous trees and perennial grassland.

@@

\begin{table}[t]
  \caption{Estimated total biomass reduction in \unit{\%} for temperature acclimation \emph{boreal} with bespoke GS and SWP=off. The uncertainty ranges reported here correspond to maximum a divergence deducted from varying the extent of stomatal opening at low light intensities and SWP=on. For comparison, the corresponding biomass reduction for the generic default MM averaged over both years is shown. The reported standard deviation is computed from all sensitivity simulations ($\pm 20\,\unit{\%}$ in extent of stomatal opening at low light, SWP on/off, and bespoke GS).}
  \label{tab:biomass_reduction}
\begin{tabular}{lllll}
\tophline
Year & \multicolumn{4}{c}{PFT}\\
& Deciduous tree& Coniferous tree & \multicolumn{2}{c}{Perennial grassland}\\
\middlehline
2018 & $15.5^{+(1.9...2.1)}_{-(0.8...1.5)}$ & $2.5^{+0.2}_{-0.2}$ & $9.7^{+0.2}_{-0.2}$ & $^*12.4^{+0.2}_{-0.2}$\\
2019 & $17.4^{+2.5}_{-1.8}$ & $3.0^{+0.2}_{-0.3}$ & $10.5^{+(0.1...0.2)}_{-(0.0...0.1)}$ & $^*13.7^{+(0.1...0.3)}_{-(0.1...0.3)}$\\
\middlehline
$\left<\mathrm{MM}\right>$ & $11.2\pm 1.1$ & $2.31\pm 0.04$ & $7.5\pm 0.9$ & $^*9.6\pm 1.4$\\
\bottomhline
\end{tabular}
\belowtable{$^*$ above ground biomass} % Table Footnotes
\end{table}

>>>>

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and assess the monthly significance of the ozone concentration anomalies in 2018/19 (Fig.~\ref{fig:anomalies_svanvik}d)). The resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month in Fig~\ref{fig:data_svanvik_2018_2019}. Negative deviations from climatology are shown as a negative percentage. Note that missing bars for certain months are both due to data availability and anomalies not meeting the $1\sigma$ criteria. The the star indicates resulting anomalies after the reconstruction of missing data in July. In April/May 2018, ozone was significantly enhanced, while no significant enhancement is found in 2019. In both years, ozone concentrations were significantly lower than average in November. These results mean, that the extensive forest fires in Sweden did not lead to a significant enhancement in \chem{[O_3]} at Svanhovd in 2018. However, there are indications that the sites further south at Esrange and Pallas experienced more days with elevated ozone in 2018 than Svanvik.

@@

We define two different hypothetical temperature acclimation: \emph{subarctic} and \emph{cold}. The most extreme of the two acclimations is \emph{subarctic}. For either, we assume that the hypothetical species are more tolerant to cold conditions and shift $f_\mathrm{T}$ towards colder temperatures accordingly. We construct \emph{cold} as representative for a species that is more tolerant to cold temperatures, but slightly less efficient at warm temperatures compared to MM. In the same way, \emph{subarctic} refers to a hypothetical species which is very tolerant to cold but is sensitive to high temperatures, and most efficient at cool temperatures ($T_\mathrm{opt}$ close to the climatological mean temperature of 1992--2000). For perennial grassland the resulting response functions are depicted together with the PDF of temperature in Fig.~\ref{fig:f_temp_grassland}a).

Norway spruce was experimentally found to be active already at rather low air temperatures and could reach $60\,\unit{\%}$ photosynthetic activity as early as \unit{doy}~100 \citep{TB:Kolari2007, TP:Wallin2013}. Based on the time series of observed \chem{CO_2} uptake and temperature at two observation sites in Southern ($\rightarrow$ \emph{cold}) and Northern ($\rightarrow$ \emph{subarctic}) Finland \citep{TB:Kolari2007}, we estimate $10\,\unit{^\circ C}\le T_\mathrm{opt} \le 15\,\unit{^\circ C}$. We assume a similar acclimation for deciduous trees. All bespoke temperature parameters are listed in Table~\ref{tab:sensitivity_tests_temp}.\\

@@

\begin{table}[t]
  \caption{Bespoke temperature parameterizations. MM refers to mapping manual \citep{GCB:Mills2011,ICP:MappingManual2017}.}
  \label{tab:sensitivity_tests_temp}
  \begin{tabular}{llrrr}
    \tophline
    Species & type & $T_\mathrm{min}$ & $T_\mathrm{opt}$ & $T_\mathrm{max}$ \\
    \middlehline
    \multirow{3}{*}{Deciduous tree} & MM & 5 & 20 & 100\\
    & Cold & 5 & 15 & 100\\
    & Subarctic & 0 & 10 & 100\\
    \middlehline
    \multirow{3}{*}{Coniferous tree} & MM & 0 & 20 & 100\\
    & Cold & 0 & 15 & 100\\
    & Subarctic & 0 & 10 & 100\\
    \middlehline
    \multirow{3}{*}{Perennial grassland} & MM & 10 & 24 & 36\\
    & Cold & 5 & 15 & 36\\
    & Subarctic & 0 & 10 & 24\\
    \bottomhline
    \end{tabular}
\end{table}

@@

As indicated above, a better acclimation will result in a higher average $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$. To quantify the resulting bespoke parameterizations, we propose the following metric. For a generic GS (May--August), we compute climatological average and standard deviation of $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$ (Eq.~(\ref{eq:stomatal})) at noon (averaged over $11\,\unit{am}-1\,\unit{pm}$ local time) and in the morning (averaged over $5-9\,\unit{am}$ local time). We presume that relative stomatal conductance of around noon (highest light intensity) and in the early morning (lower intensities) are good proxies for \chem{CO_2} uptake efficiency. Our arbitrary optimization target is $60\,\unit{\%}$. Additional constrains are a small deviation between noon and morning and a low standard deviation indicating a higher robustness to interannual variability of growing conditions. For simplicity, we neglect the dependency on SWP in this regard. From the results shown in Fig.~\ref{fig:javis_func_opt_mean}, we identify \emph{subarctic}, PPFD0.8 as the best acclimation for all hypothetical species or PFTs alike. As expected due to the small adjustments, coniferous trees display the lowest deviation between the different types of parameterizations, while the divergence for perennial grassland is substantial as response to the stronger proposed temperature acclimation.

@@

For deciduous trees (Fig.~\ref{fig:pody_rel}a) all simulations exceed the CL by $5-25\,\unit{mmol\,\chem{O_3}\,m^{-2}}$. Deciduous trees display the largest variance of ozone uptake among all species or PFTs ($10-31\,\unit{mmol\,\chem{O_3}\,m^{-2}}$). In particular, the sensitivity to the light threshold is especially pronounced, e.g. $\Delta\mathrm{POD_1} = ^{+2.5}_{-3.6}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in case of the subarctic type without bespoke GS in 2019. Without bespoke GS, 2018 displays a higher ozone damage risk than 2019. However, taking the later start and overall shorter GS in 2018 into account, this is reversed for the \emph{subarctic} acclimation type. This can be partly explained by very high light response factors (over $f_\mathrm{light}>0.8$) in the beginning of the GS in these simulations. Whether this is a bug or a feature of the $\mathrm{DO_3SE}$ model is not clear. SWP induced reduction in ozone uptake is only effective in 2018 and without bespoke GS. The temperature acclimation dependent bias in ozone uptake deduced for bespoke GS ranges between $(1.4-3.6)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(2.7-7.7)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+1.6}_{-2.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+1.9}_{-2.7}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

For coniferous trees (Fig.~\ref{fig:pody_rel}b), most simulations slightly exceed the CL ($0-10\,\unit{mmol\,\chem{O_3}\,m^{-2}}$). Coniferous trees' acclimation to prevailing temperatures was already good from the beginning and therefore the least biased of the generic MM parameterization. Coniferous trees display a medium sensitivity to the variation in the light threshold, e.g. $\Delta\mathrm{POD_1} = ^{+1.7}_{-1.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in case of subarctic type without bespoke GS in 2018. Taking the bespoke GS into account, we find a higher ozone uptake in 2019 for all bespoke temperature response functions. The overall bias deduced from bespoke GS for subarctic and cold types with respect to MM ranges between $(0.5-1.0)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(2.0-3.3)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+1.0}_{-0.8}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+1.3}_{-1.0}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

For perennial grassland (Fig.~\ref{fig:pody_rel}c), all simulations with bespoke GS stay below the CL. Perennial grassland shows the smallest ozone uptake, but a similarly large bias as deciduous trees. We also find a reversal for predicted ozone damage risk in $\mathrm{POD_1}$ between 2018 and 2019 for the subarctic type. Perennial grassland shows the lowest sensitivity to the light threshold and SWP is only relevant without bespoke GS. The overall bias deduced from bespoke GS for subarctic and cold types with respect to MM ranges between $(2.2-3.4)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2018 and $(4.4-6.4)\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ in 2019. The maximum systematic deviations deduced from the $-20\,\unit{\%}$ (superscript) and $+20\,\unit{\%}$ (subscript) variation of the extent of stomatal opening at low light intensities amount to $^{+0.3}_{-0.2}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$ and $^{+0.3}_{-0.3}\,\unit{mmol\,\chem{O_3}\,m^{-2}}$, respectively.

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig11}
  \caption{$\mathrm{DO_3SE}$ modeling results for $\mathrm{POD_1}$ with default parameterization (MM) and bespoke parameters for Svanhovd. Bespoke parameterizations include temperature response functions for subarctic, cold and light thresholds (PPFD0.8, PPFD1.2) at the end of a MM GS (lighter hue and dotted lines) and the estimated GS for Svanhovd (2018, 2019). (a) Deciduous tree; (b) coniferous tree; (c) perennial grassland. The dashed horizontal lines indicate critical levels defined in \citet{ICP:MappingManual2017,ESPR:Hayes2021} for each species, respectively.}
  \label{fig:pody_rel}
\end{figure}

We estimated the biomass reductions in accordance to the CLs in \citet{ICP:MappingManual2017, ESPR:Hayes2021} for the most extreme temperature acclimation (\emph{subarctic}) for each bespoke PFT. The estimates are listed in Table~\ref{tab:biomass_reduction}. The reported range in uncertainty corresponds to the maximum deviation defined by the $\pm 20\,\unit{\%}$ variation of the extent of stomatal opening at low light intensities with SWP=on. For deciduous trees and perennial grassland, substantial reductions in total biomass in comparison with the default generic MM parameterizations are predicted for both years. Coniferous trees are the least affected and the magnitude of total biomass reduction is independent of the choice of the parameterization within given uncertainties. This may reflect the more comprehensive research on this species or PFT feeding into the generic MM parameterization. The systematic deviation for deciduous trees is one order of magnitude larger than for coniferous trees and perennial grassland.

@@

\begin{table}[t]
  \caption{Estimated total biomass reduction in \unit{\%} for temperature acclimation \emph{subarctic} with bespoke GS and SWP=off. The uncertainty ranges reported here correspond to maximum a divergence deducted from varying the extent of stomatal opening at low light intensities and SWP=on. For comparison, the corresponding biomass reduction for the generic default MM averaged over both years is shown. The reported standard deviation is computed from all sensitivity simulations ($\pm 20\,\unit{\%}$ in extent of stomatal opening at low light, SWP on/off, and bespoke GS).}
  \label{tab:biomass_reduction}
\begin{tabular}{lllll}
\tophline
Year & \multicolumn{4}{c}{PFT}\\
& Deciduous tree& Coniferous tree & \multicolumn{2}{c}{Perennial grassland}\\
\middlehline
2018 & $15.5^{+(1.9...2.1)}_{-(0.8...1.5)}$ & $2.5^{+0.2}_{-0.2}$ & $9.7^{+0.2}_{-0.2}$ & $^*12.4^{+0.2}_{-0.2}$\\
2019 & $17.4^{+2.5}_{-1.8}$ & $3.0^{+0.2}_{-0.3}$ & $10.5^{+(0.1...0.2)}_{-(0.0...0.1)}$ & $^*13.7^{+(0.1...0.3)}_{-(0.1...0.3)}$\\
\middlehline
$\left<\mathrm{MM}\right>$ & $11.2\pm 1.1$ & $2.31\pm 0.04$ & $7.5\pm 0.9$ & $^*9.6\pm 1.4$\\
\bottomhline
\end{tabular}
\belowtable{$^*$ above ground biomass} % Table Footnotes
\end{table}
